---
title: "Week 4 Homework, Unit 1"
author: "Lemi Daba"
date: "3/7/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(lfe)
library(stargazer)

tea_data <- read_csv("tea_data_corrected.csv")
```


## Question 1

First, lets understand the data structure. What describes the unit of observation in the data?


### Answer

```{r}
tea_data 
```

It appears each observation represents a cohort in each county.

```{r}
tea_data %>% count(admin, biryr)
```

The above result strengthens our suspicion (the number of observations and the number of unique county-cohort combination is the same). To confirm, let's see if there is more than one observation in any county-cohort combination:

```{r}
tea_data %>% 
    count(admin, biryr) %>% 
    filter(n > 1)
```

Hence, we can now be sure that each observation represents a particular cohort in a given county.


## Question 4a

Now, generate the variable `teaDum`, which takes value 1 if any amount of tea is sown and 0 otherwise. Generate the variable `post`, which takes a value of 1 if the cohort is born on or after 1979. To be sure that you generated this variables correctly, the mean of `teaDum` is 0.209 and mean of `post` is 0.412. Now, also generate the interaction term.

Estimate $ \gamma $ from the data. Give its point estimate and the standard error.


### Answer

```{r}
tea_data <- tea_data %>%
  mutate(
    teaDum = (teasown > 0),
    post = (biryr >= 1979)
  ) 

tea_data %>%
  summarise(
    mean_tea = mean(teaDum, na.rm = TRUE),
    mean_post = mean(post, na.rm = TRUE)
  )
```


We now estimate the model in Question 2.

```{r message=FALSE, warning=FALSE}
reg1 <- lm(sex ~ teaDum*post, data = tea_data)

stargazer(reg1, type = "text", digits = 5)
```

## Question 6a

Now generate variables `orchardDum` and `cashcropDum` in a way similar to `teaDum` (that is, they take value 1 if the crop is grown and 0 otherwise). Also, generate the interactions with post. Estimate the following regression:

$$
 S_{ij} = \alpha + \beta_1TeaDum_i + \beta_2OrchardDum_i + \beta_3cashcropDum_i + \gamma_1(TeaDum_i\times Post_i) + ...
$$

What are the point estimates for each of $ \gamma_1 $, $ \gamma_2 $, and $ \gamma_3 $?

### Answer

```{r message=FALSE, warning=FALSE}
tea_data <- tea_data %>%
  mutate(
    orchardDum = (orch > 0),
    cashcropDum = (cashcrop > 0)
  )

reg2 <- lm(
  sex ~ (teaDum + orchardDum + cashcropDum) * post,
  data = tea_data
)

stargazer(reg2, type = "text", digits = 6)
```

## Question 8

Now instead of grouping all the pre- and post-cohorts and grouping all the counties into two groups (those who grow and don't), let's exploit all the variation in the data. That is, let us estimate:

...

What is the estimate of $ \gamma_1 $ from this model? (Please provide your answer to 3 significant figures.) Does this change the conclusion from the previous regressions?

### Answer

```{r}
reg3a <- felm(
  sex ~ I(post * teaDum) + I(post * orchardDum) + I(post * cashcropDum) | admin + biryr,
  data = tea_data
)

stargazer(reg3a, type = "text")
```

Let's try it the old way (this takes longer).

```{r}
reg3b <- lm(
  sex ~ I(post * teaDum) + I(post * orchardDum) + I(post * cashcropDum) + as.factor(admin) + as.factor(biryr),
  data = tea_data
)

stargazer(reg3b, type = "text", keep = c("tea", "orch", "cash"))
```


Comparing the two:
```{r}
stargazer(reg3a, reg3b, type = "text", keep = c("tea", "orch", "cash"))
```













