---
title: "Week 3 Homework, Unit 1"
author: "Lemi Daba"
date: "2/25/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r message=FALSE, warning=FALSE}
# Some basic set-up
library(dummies)
library(AER)
library(tidyverse)

# Load the data
inpres <- read_csv("inpres_data_corrected.csv")
```

## Question 1

Run a regression of log monthly earnings on education. What is the estimated impact of an extra year of education on log monthly earnings?

### Answer

```{r}
lm(log_wage ~ education, data = inpres) %>% summary()
```

## Question 3

First we will estimate the impact of the program on educational attainment using difference in differences. People born in 1968 or later were exposed to the program. Generate a dummy variable that takes the value 1 if the person was born in these years and 0 otherwise. We will construct a difference-in-differences table with four cells across low/high program intensity and old/young (unexposed/exposed). Fill in the table with the average education level for that group. Your table should be similar to Table 3 Panel A in the paper. For now, do not worry about standard errors. (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912.)


### Answer

```{r message=FALSE}
summ <- inpres %>%
  mutate(born_aft68 = (birth_year >= 68)) %>%
  group_by(high_intensity, born_aft68) %>%
  summarise(mean_educ = mean(education))

summ
```


```{r}
X <- cbind(
  c(
    summ$mean_educ[4],
    summ$mean_educ[3],
    summ$mean_educ[4] - summ$mean_educ[3]
  ),
  c(
    summ$mean_educ[2],
    summ$mean_educ[1],
    summ$mean_educ[2] - summ$mean_educ[1]
  ),
  c(
    summ$mean_educ[4] - summ$mean_educ[2],
    summ$mean_educ[3] - summ$mean_educ[1],
    (summ$mean_educ[4] - summ$mean_educ[3]) - (summ$mean_educ[2] - summ$mean_educ[1])
  )
)

colnames(X) <- c(
  "High Intensity (Treatment)",
  "Low Intensity (Control)",
  "Difference (Treatment-Control)"
)

rownames(X) <- c(
  "**Young (Born 1968 or later)**",
  "**Old (Born before 1968)**",
  "**Difference (Young - Old)**"
)

knitr::kable(X, digits = 2)
```


## Question 4

Consider only the regions where many schools were build due to INPRES (high intensity). What is the average difference in outcomes between people who were young enough to take advantage of the schools and those who were too old to benefit from the schools? (Please round to the nearest hundredth).

*Thought exercise: Under what assumptions would this be an unbiased estimate of the causal effect of the program on education? Do you think this is an unbiased estimate in this case?*

### Answer

```{r message=FALSE}
inpres %>% 
  mutate(born_aft68 = (birth_year >= 68)) %>% 
  filter(high_intensity == 1) %>% 
  group_by(born_aft68) %>% 
  summarise(avg_educ = mean(education) %>% round(2)) %>% 
  mutate( diff = (.$avg_educ[2] - .$avg_educ[1]) %>% round(2) )
```


## Question 5

Now consider only people who were young enough to be exposed to the INPRES program. What is the average difference in education between such people in regions with high and low program intensity? (Please round to the nearest hundredth).

*Thought exercise: Under what assumptions would this be an unbiased estimate of the causal effect of the program on education? Do you think this is an unbiased estimate in this case?*

### Answer

```{r message=FALSE}
inpres %>% 
  mutate(born_aft68 = (birth_year >= 68)) %>% 
  filter(born_aft68 == TRUE) %>% 
  group_by(high_intensity) %>% 
  summarise(avg_educ = mean(education) %>% round(2)) %>% 
  mutate(diff = (.$avg_educ[2] - .$avg_educ[1]) %>% round(2))
```


## Question 6

What is the DD estimate of the effect of the program on education? (Please round to the nearest hundredth).

*Thought exercise: Under what assumptions would this be an unbiased estimate of the causal effect of the program on education? Do you think this is an unbiased estimate in this case?*

### Answer

```{r message=FALSE}
DD_est <- (summ$mean_educ[4] - summ$mean_educ[3]) - (summ$mean_educ[2] - summ$mean_educ[1])
DD_est %>% round(2)
```


















