---
title: "Week 8 Homework, Unit 1"
author: "Lemi Daba"
date: "3/25/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Load necessary packages
library(tidyverse)
library(haven)
library(stargazer)
library(fastDummies)
library(broom)
library(car)
```


```{r}
# Read and view the data
paxson <- read_dta("paxson.dta")
paxson
```


## Question 4

Using the coefficients estimated in the regression for Table 3, Column 1, Paxson constructs a predicted value for permanent income as follows. She multiples the permanent characteristics by their respective coefficients, and adds them up to form **incperm** (see equation 2 on page 17 of the paper.) Generate the variable **incperm**. What is the standard deviation of **incperm**?

**R Hint: You can store the *summary()* of a linear model, then use *coef()* to generate a table of coefficients. To get a specific coefficient, use *coef(reg_sum)[‘’x’’,‘‘Estimate’’]*.**

### Answer

Let's first replicate the regression results on Table 3. I'll use the `dummy_cols()` function from the `fastDummies` package to generate region and year dummies.

```{r}
# Selecting variables in the order they are in Table 3
paxson4reg <- paxson %>% 
  select( inc, year, region, p0to5, 
          starts_with( c("dev", "dvsq", "m", "f", "of")), -month ) %>% 
  dummy_cols( c("year", "region") , remove_first_dummy = TRUE) %>% 
  select(inc, year_81, year_86, dev1, dvsq1, dev2, dvsq2, 
         dev3, dvsq3, dev4, dvsq4, p0to5, m12, f12, m18, f18, m18elem,
         m18sec, m18pos, f18elem, f18sec, f18pos, m65, f65, of0, of1:of5,
         everything(), -year, -region)

# Run the regression
reginc <- lm( inc ~ ., data = paxson4reg )  
stargazer(reginc, type = "text", keep = "^(region)") # ??
```

Let's use the `tidy()` command from the package `broom` to extract the coefficients of the above regression.

```{r}
coefs <- tidy(reginc) %>% 
  select(term, estimate)
coefs
```

We can compute the estimate of permanent income using matrix multiplication. 

```{r}
# Select the appropriate variables according to equation 2 on the paper
X <- paxson4reg %>% 
  select(-inc, -(dev1:dvsq4)) %>% 
  as.matrix()

b <- coefs %>%
  filter( !str_detect(term, "^\\(|dev|dvsq") ) %>%
  column_to_rownames(var = "term") %>% 
  as.matrix()

# Check compatibility
identical(colnames(X), rownames(b))
```

```{r}
# Generate "incperm"
paxson <- paxson %>% 
  mutate(incperm = X %*% b)
```


We can now compute the standard deviation of `incperm`.

```{r}
sd(paxson$incperm)
```

## Question 6

What is the standard deviation of **inctrans**?

### Answer

We can generate `inctrans` in a similar way. As before, we need to extract the relevant variables according to equation 3 on the paper.

```{r}
Y <- paxson4reg %>%
  select(year_81:dvsq4) %>%
  as.matrix()

c <- coefs %>%
  filter( str_detect(term, "^year|dev|dvsq") ) %>%
  column_to_rownames(var = "term") %>% 
  as.matrix()

# Check compatibility
identical(colnames(Y), rownames(c))
```

```{r}
# Generate "inctrans"
paxson <- paxson %>% 
  mutate(inctrans = Y %*% c)

sd(paxson$inctrans)
```

## Question 7

Paxson also has a category called unexplained income, defined as **inc – incperm – inctrans**. Form this variable and call it **incunexp.** What is the standard deviation of **incunexp**?

### Answer

```{r}
paxson <- paxson %>% 
  mutate(incunexp = inc - incperm - inctrans)

sd(paxson$incunexp)
```

## Question 8

You will now run a regression to estimate the effect of income on savings. Use the variable **save2** as your measure of savings. Include the variables that you included in the matrix for the final regression (see the explanation to question 4 above.) What do you estimate for the marginal propensity to save out of each additional dollar of transitory income (i.e. **inctrans**)?


### Answer

```{r warning=FALSE}
save2reg <- lm(
  save2 ~ incperm + inctrans + incunexp + p0to5 + p6to11 + p12to17 + p18to64 +
    p65 + sd1 + sd2 + sd3 + sd4 + factor(year), data = paxson
)

stargazer(save2reg, type = "text")
```

Hence, the marginal propensity to save out of transitory income is 0.804. This result is the same as the one in Table 4 of the paper.


## Question 9

What do you estimate for the marginal propensity to save out of each additional dollar of permanent income (i.e. **incperm**)?

### Answer

From the regression in Question 8, the MPS for permanent income is 0.440.


## Question 10

Test the null hypothesis that the marginal propensity to save out of each dollar of transitory income from question 8 equals the marginal propensity to save out of each dollar of permanent income from question 9. Can we reject the null hypothesis at 95% significance level?

*R Hint: Use the __linearHypothesis()__ command from the “car” library, which you were asked to install in the explanation to question 3 above. Note that testing whether two coefficients are equal is equivalent to testing whether one minus the other equals 0.*


### Answer

```{r}
linearHypothesis(save2reg, "incperm = inctrans")
```

Since the p-value is 0.028 which is less than 0.05, we reject the equality of their coefficients at the 95 percent significance level.



















