---
title: "Week 10 Homework"
author: "Lemi Daba"
date: "4/15/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}
# Load required packages
library(tidyverse)
library(stargazer)
```

```{r message=FALSE}
# Load the data:
mitadata <- read_csv("mitaData_corrected.csv")
mitadata
```

The following function enables us to run regressions with clustered standard 
errors for different running variables and different cutoff points. The packages
`lmtest` and `multiwayvcov` need to be installed first to define and use this function.
```{r}
mita_cluster_regs <- function(vars, cutoff) {
  require(multiwayvcov, quietly = TRUE)
  require(lmtest, quietly = TRUE)

  # Run OLS without clustering 
  if (all(vars == c("x", "y"))) {
    mitareg <- lm(
      formula = lhhequiv ~ pothuan_mita + poly(x, 3, raw = TRUE) +
        poly(y, 3, raw = TRUE) + I(x * y) + I((x^2) * y) + I(x * (y^2)) +
        elv_sh + slope + infants + children + adults + bfe4_1 + bfe4_2 + bfe4_3,
      data = mitadata,
      subset = (d_bnd < cutoff)
    )
  } else if (vars == "dpot") {
    mitareg <- lm(
      formula = lhhequiv ~ pothuan_mita + poly(dpot, 3, raw = TRUE) +
        elv_sh + slope + infants + children + adults + bfe4_1 + bfe4_2 + bfe4_3,
      data = mitadata,
      subset = (d_bnd < cutoff)
    )
  } else {
    stop('Enter either `c("x", "y")` or `"dpot"` for `vars` ', call. = FALSE
    )
  }

  # Get the clustered Variance-covariance matrix:
  mita.vcovCL <- cluster.vcov(
    mitareg,
    mitadata %>% filter(d_bnd < cutoff) %>% select(district)
  )

  # Return the result with clustered standard errors:
  res <- coeftest(mitareg, mita.vcovCL)
  return(res)
}
```

Let's run the regressions.
```{r message=FALSE}
xy_100 <- mita_cluster_regs(c("x", "y"), 100)
xy_75 <- mita_cluster_regs(c("x", "y"), 75)
xy_50 <- mita_cluster_regs(c("x", "y"), 50)
```

We summarize the results together in the following table.
```{r warning=FALSE}
stargazer(xy_100, xy_75, xy_50,
  type = "text",
  keep = "pothuan_mita",
  title = "Cubic Polynomial in Latitude and Longitude",
  column.labels = c("<100 km", "<75 km", "<50 km"),
  style = "aer"
)
```

As can be seen, all coefficients, corresponding to the different cutoff values,
are statistically insignificant at the 5% level.

## Question 3

What is the coefficient estimate for Mita on the regression using 100km as the relevant cutoff? (Please input your answer to 3 decimal places).

### Answer

`-0.284`

## Question 4

Is this result significant at the 5% level?

### Answer

No.

## Question 5

What is the coefficient estimate for Mita on the regression using 75km as the relevant cutoff? (Please input your answer to 3 decimal places).

### Answer

`-0.216`

## Question 6

Is this result significant at the 5% level?

### Answer

No

## Question 7

What is the coefficient estimate for Mita on the regression using 50km as the relevant cutoff? (Please input your answer to 3 decimal places).

### Answer

`-0.331`

## Question 8

Is this result significant at the 5% level?

### Answer

No

---

Run the same regressions as before, but instead of polynomial terms in longitude and latitude, use a cubic polynomial in distance to Potosi dpot. That is, include the first, second and third powers of this variable in the regressions. Again, cluster the standard errors by district and run the regression in 3 ways: first, for observations where the distance to Mita boundary (d_bnd) is less than 100km, next when it is less than 75km, and lastly when it is less than 50km.

---

Let's run the corresponding regressions with `dpot` as the running variable.
```{r}
dpot_100 <- mita_cluster_regs("dpot", 100)
dpot_75 <- mita_cluster_regs("dpot", 75)
dpot_50 <- mita_cluster_regs("dpot", 50)
```

The following table summarizes the relevant results.


## Question 9

What is the coefficient estimate for Mita on the regression using 100km as the relevant cutoff? (Please input your answer to 3 decimal places).

```{r warning=FALSE}
stargazer(dpot_100, dpot_75, dpot_50, type = "text", 
          keep = "pothuan_mita",
          title = "Cubic Polynomial in Distance to Potosi",
          column.labels = c("<100 km", "<75 km", "<50 km"),
          style = "aer")
```

All results are significant at the 1% (hence, at the 5%) level.

## Question 9

What is the coefficient estimate for Mita on the regression using 100km as the relevant cutoff? (Please input your answer to 3 decimal places).

### Answer

`-0.337`

## Question 10

Is this result significant at the 5% level?

### Answer

Yes

## Question 11

What is the coefficient estimate for Mita on the regression using 75km as the relevant cutoff? (Please input your answer to 3 decimal places).

### Answer

`-0.307`

## Question 12

Is this result significant at the 5% level?

### Answer

Yes

## Question 13

What is the coefficient estimate for Mita on the regression using 50km as the relevant cutoff? (Please input your answer to 3 decimal places).

### Answer

`-0.329`

## Question 14

Is this result significant at the 5% level?

### Answer

Yes




















































