---
title: "Week 1 Homework, Unit 2"
author: "Lemi Daba"
date: "2/14/2021"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


```{r}
# Some basic set-up
library(tidyverse)
devt <- read_csv("wb_dev_ind.csv")
```




## Question 1

What is the Mean of **GDP per capita**? What is the standard deviation of GDP per capita? (Please round to the nearest whole number. For instance, 1235 would be accepted if the correct answer 1234.56)

### Answer

```{r}
devt
```


```{r}
summary(devt)
```

```{r}
devt %>% summarise(
  mean_gdpPc = mean(gdp_per_capita, na.rm = TRUE) %>% round(),
  sd_gdpPc = sd(gdp_per_capita, na.rm = TRUE) %>% round()
)
```


## Question 2

What is the mean **illiteracy rate** across all countries? What is the standard deviation? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt %>%
  mutate(ILliteracy_all = 100 - literacy_all) %>%
  summarise(
    mean_ILLit = mean(ILliteracy_all, na.rm = TRUE) %>% round(2),
    sd_ILLit = sd(ILliteracy_all, na.rm = TRUE) %>% round(2)
  )
```

## Question 3

What is the mean **infant mortality rate** across all countries? What is the standard deviation? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt %>%
  summarise(
    mean_INF_mortal = mean(infant_mortality, na.rm = TRUE) %>% round(2),
    sd_INF_mortal = sd(infant_mortality, na.rm = TRUE) %>% round(2)
  )
```

## Question 4

What is the mean male illiteracy rate? What is the mean female illiteracy rate? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt %>%
  mutate(
    ILLit_male = 100 - literacy_male,
    ILLit_female = 100 - literacy_female
  ) %>%
  summarise(
    mean_ILLit_male = mean(ILLit_male, na.rm = TRUE) %>% round(2),
    mean_ILLit_female = mean(ILLit_female, na.rm = TRUE) %>% round(2)
  )
```

---
For questions 5 to 8, restrict your dataset to countries for which we have GDP per capita information.

---

```{r}
devt_gdp <- devt %>%
  filter(!is.na(gdp_per_capita))
```

## Question 5

What are the mean, minimum, and maximum **illiteracy rate** among the 50 richest countries? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt_gdp %>%
  arrange(desc(gdp_per_capita)) %>%
  filter(row_number() <= 50) %>%
  mutate(ILLiteracy_all = 100 - literacy_all) %>%
  summarise(
    mean_ILLit_rich = mean(ILLiteracy_all, na.rm = TRUE) %>% round(2),
    min_ILLit_rich = min(ILLiteracy_all, na.rm = TRUE) %>% round(2),
    max_ILLit_rich = max(ILLiteracy_all, na.rm = TRUE) %>% round(2)
  )
```

## Question 6

What are the mean, minimum, and maximum **illiteracy rate** among the 50 poorest countries? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt_gdp %>%
  arrange(gdp_per_capita) %>%
  filter(row_number() <= 50) %>%
  mutate(ILLiteracy_all = 100 - literacy_all) %>%
  summarise(
    mean_ILLit_poor = mean(ILLiteracy_all, na.rm = TRUE) %>% round(2),
    min_ILLit_poor = min(ILLiteracy_all, na.rm = TRUE) %>% round(2),
    max_ILLit_poor = max(ILLiteracy_all, na.rm = TRUE) %>% round(2)
  )
```

## Question 7

What are the mean, minimum, and maximum **infant mortality rate** among the 50 richest countries? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt_gdp %>%
  arrange(desc(gdp_per_capita)) %>%
  filter(row_number() <= 50) %>%
  summarise(
    mean_INFmortal_rich = mean(infant_mortality, na.rm = TRUE) %>% round(2),
    min_INFmortal_rich = min(infant_mortality, na.rm = TRUE) %>% round(2),
    max_INFmortal_rich = max(infant_mortality, na.rm = TRUE) %>% round(2)
  )
```

## Question 8

What are the mean, minimum, and maximum infant mortality rate among the 50 poorest countries? (Please round to the nearest hundredth. For instance, 67.89 would be accepted if the correct answer is 67.8912)

### Answer

```{r}
devt_gdp %>%
  arrange(gdp_per_capita) %>%
  filter(row_number() <= 50) %>%
  summarise(
    mean_INFmortal_poor = mean(infant_mortality, na.rm = TRUE) %>% round(2),
    min_INFmortal_poor = min(infant_mortality, na.rm = TRUE) %>% round(2),
    max_INFmortal_poor = max(infant_mortality, na.rm = TRUE) %>% round(2)
  )
```

---

For questions 9-15, return to using the original (unrestricted) data set.

---

## Question 9

What is the **median** GDP per capita? (Please round to the nearest whole number.)

### Answer

```{r}
devt %>%
  summarise(median_gdpPc = median(gdp_per_capita, na.rm = TRUE) %>% round())
```

## Question 10

Regress the infant mortality rate on per capita GDP, and then answer questions 10-12.

### Answer

```{r}
lm(infant_mortality ~ gdp_per_capita, data = devt) %>% summary()
```

## Question 13

Regress the illiteracy rate on GDP per capita. Is the coefficient on per capita GDP significantly different from zero at the 5% level?

### Answer

```{r}
lm(I(100 - literacy_all) ~ gdp_per_capita, data = devt) %>% summary()
```

## Question 14

Regress the infant mortality rate on the illiteracy rate. Graph a scatter plot of the data as well as the regression line.

### Answer

```{r}
lm(infant_mortality ~ I(100 - literacy_all), data = devt) %>% summary()
```

```{r}
devt %>%
  mutate(ILLiteracy_rate = 100 - literacy_all) %>%
  ggplot(aes(ILLiteracy_rate, infant_mortality)) +
  geom_point() +
  geom_smooth(se = FALSE, method = "lm")
```

















